Viscous Transport in Eroding Porous Media

### 2019-07-23 docs/transport/erosion_transport.tex
working on erosion paper

@@

Equation~\eqref{eqn:laplaceComplex} can be converted to a Cauchy
integral by first finding boundary data of $v$ which satisfies the
Sokhotski-Plemelj jump relation
\begin{align}
  \label{eqn:SPrelation}
  v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
Once the boundary data of $v$ is formed, we have
\begin{align}
  \label{eqn:cauchy}
  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \quad
  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \quad
  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy.
\end{align}
for $x \in \Omega$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tortuosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The tortuosity of a geometry quantifies the average amount of turning
made by a streamline.  Mathematically, it is defined as
\begin{align}
  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
  {\displaystyle\int_{S}u_x(y)\,dy},
  \label{eqn:tortuosity1}
\end{align}
where $S$ is an cross-section perpendicular to the $x$ axis with length
$d$, $\lambda(y)$ is the length of the streamline that is initialized
at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
the velocity at the $y$-coordinate along $S$.  Under the assumptions
that the flow is incompressible and not reentrant, the tortuosity can be
equivalently measured as~\cite{dud-koz-mat2011}
\begin{align}
  T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
           {\displaystyle\int_\Omega u_x(\yy)\, d\yy}.
  \label{eqn:tortuosity2}
\end{align}
The flow is reentrant if all streamlines connect the inlet to the
outlet.  Recirculation zones are possible in viscous fluids, but they
only constitute a small fraction of the total porous media.  Therefore,
the tortuosity defined in equation~\eqref{eqn:tortuosity2} is an upper
bound for the definition in equation~\eqref{eqn:tortuosity1}.  We have
used formulas for a particular geometry, and the difference is
negligible.  Since equation~\eqref{eqn:tortuosity2} does not require the
additional work of computing particle trajectories, we use this
definition for the tortuosity.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Gap Distribution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{s:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We have shown that the velocity, shear stress, vorticity, and pressure
of the double-layer potential can all be written in terms of Cauchy
integrals and its first two derivatives.  Therefore, we require
quadrature methods to evaluate the expressions in
equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
periodic, the trapezoid rule has spectral accuracy.  However, the
integrand becomes nearly singular as $x$ approaches $\bd\Omega$, and the
quadrature error is arbitrarily large for a fixed resolution.  There
have been a variety of near-singular integration schemes developed, and
we extend a method first outlined by Barnett et
al.~\cite{bar-wu-vee2015} which we call the {\em Barycentric quadrature
rule}.  This method first uses the density function $\tau(y)$ to compute
the boundary data of $v$, denoted by $v^-(y)$.  Then, it makes use of
the identity
\begin{align}
  v(x) = \int_{\bd\Omega} \frac{v^{-}(y)}{y-x} \, dy, 
  \quad x \in \Omega.
\end{align}

Here, we briefly describe the Barycentric quadrature method, and then
derive a necessary extension to simulate erosion.  The method starts
with a quadrature rule with nodes $y_j \in \bd\Omega$ and weights $w_j$,
$j=1,\ldots,N$.  We use the trapezoid rule because of its superior
accuracy when $x$ is sufficiently far from $\bd\Omega$.  However, at a
fixed resolution, if $x$ is sufficiently close to $\bd\Omega$, each of
the integrands in equation~\eqref{eqn:cauchy} are nearly-singular and
the quadrature error is prohibitively large.  However, the trapezoid
rule applied to the identity
\begin{align}
  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0,
\end{align}
has a uniformly bounded error since the integrand is not nearly-singular
as $x$ approaches $\bd\Omega$.  That is,
\begin{align}
  \sum_{j=1}^{N} \frac{v^{-}(y_j) - v(x)}{y_j - x} w_j \approx 0.
\end{align}
Rearranging for $v(x)$, we have
\begin{align*}
  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j},
\end{align*}
which is simply the trapezoid rule applied to the two integrals in the
identity
\begin{align}
  v(x) = \frac{\int\limits_{\bd\Omega} \frac{v^{-}(y)}{y-x}\, dy}
    {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy}.
\end{align}
Of course, the denominator is simply $1$, but by applying the trapezoid
rule to both integrands, the result is an error with a uniform bound.
To compute $v'(x)$, the identity
\begin{align}
  v'(x) = \frac{\int\limits_{\bd\Omega} 
    \frac{v^{-}(y) - v(x)}{(y-x)^2}\, dy}
  {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy},
\end{align}
is used, and applying the trapezoid rule
\begin{align}
  v'(x) \approx \frac{\sum\limits_{j=1}^{N}
    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial Discretization}
\label{s:spatialDiscretization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
By using an integral equation formulation, we only have to discretize
the boundary of the domain.  Therefore, we only have to discretize
one-dimensional closed-curves, allowing us to use the spectrally
accurate trapezoid rule~\cite{tre-wei2014} and Fourier differentiation.
Moreover, since we only discretize the boundary of the domain, resolving
the complex eroding bodies is straightforward.

Consider eroding bodies $\gamma_k$, $k=1,\ldots,M$, in a fluid domain
$\Omega$ with boundary $\Gamma$.  Let the length of $\Gamma$ be $L_{0}$,
and the length of $\gamma_k$ be $L_k$.  We discretize each eroding body
$\gamma_k$ with $N_\iin$ points and discretize $\Gamma$ with $N_\out$
points.  The $j^{th}$ discretization point on $\Gamma$ is denoted by
$\yy_j^0$, and the $j^{th}$ discretization point on $\gamma_k$ is
denoted by $\yy^k_j$.  The discretization points are initially
distributed evenly in arclength, and this equispacing is maintained for
the entire simulation by using a {\thL}
formulation~\cite{hou-low-she1994}.  In addition, we apply mild
smoothing strategies~\cite{qua-moo2018} to avoid the corners that
erosion inevitably develop.    Since the points are equispaced, the
trapezoid rule to evaluate the velocity at a target point $\xx$ is
\begin{align}
  \label{eqn:trap}
  \uu(\xx) \approx \frac{L_0}{N_\out} \sum_{j=1}^{N_\out} 
    D(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \frac{L_k}{N_\iin} \sum_{j=1}^{N_\iin}
    D(\xx,\yy^k_j) \eeta^k_j,
\end{align}
where $D$ is the kernel of the Stokes double-layer potential defined in
Equation~\eqref{eqn:stokesDLP}.

As previously mentioned, the quadrature error of the trapezoid rule is
large if $\xx$ is close to $\bd\Omega$.  The proximity between $\xx$ and
$\bd\Omega$ occurs in dense packings, and also when evaluating the
velocity in the fluid bulk.  For these nearby points, instead of
applying the trapezoid rule, the Barycentric quadrature rule is applied.
In particular, the Stokes double-layer potential is decomposed into
Laplacian double-layer potentials~\eqref{eqn:Stokes2Laplace}.  Then, for
each of these Laplacian double-layer potentials, the density function is
used to find the boundary values of the analytic function whose real
part is the layer potential of interest~\eqref{eqn:SPrelation}.
Finally, instead of applying the trapezoid rule to compute the Cauchy
integrals, the quadrature rule outlined by Barnet et.~al is used
\begin{align}
  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}
  \quad \text{and} \quad
  v'(x) \approx \frac{\sum\limits_{j=1}^N 
    \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, 
  \label{eqn:vvpQuadrature}
\end{align}
Then, even if $x$ is close to $\bd\Omega$, the integrand is no longer
nearly-singular and the accuracy of the trapezoid rule is bounded
independent of $x$.  A similar identity identity involving $v'(x)$ also
holds.   Now, applying the spectrally accurate trapezoid rule, the
quadrature error of the Barycentric quadrature rule
is uniformly bounded~\cite{bar-wu-vee2015}.  A slight modification of
these formulae are applied if $x \in \Omega^{c}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
While accurate quadrature rules for $v(x)$ and $v'(x)$ have already been
developed~\cite{bar-wu-vee2015}, computing the shear stress and
vorticity requires a Barycentric quadrature rule for $v''(x)$.  We mimic
the approach developed in~\cite{bar-wu-vee2015}.  First, if $x \in
\Omega$ and $n \in \mathbb{N}$, then 
\begin{align}
  \frac{1}{2\pi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
  \left\{
    \begin{array}{ll}
      1, & n = 1, \\
      0, & n > 1. \\
    \end{array}
  \right.
\end{align}
Applying this identity to the Cauchy integral theorem for $v''(x)$, we
have
\begin{align}
  0 &= \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x) \\
%    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{2v^{-}(y)}{(y-x)^3}\,dy - 
%    \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{(y-x)^2 v''(x)}{(y-x)^3}\,dy -
%    \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{2v(x)}{(y-x)^3}\, dy -
%    \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{2(y-x)v'(x)}{(y-x)^3}\, dy \\
    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
      {(y-x)^3}\, dy.
\end{align}
Since we have constructed the integrand so that it is bounded for for
all $x \in \Omega$, the quadrature error of the trapezoid rule is
acceptable.  Applying the quadrature rule and solving for $v''(x)$, the
Barycentric quadrature rule for the second derivative is
\begin{align}
  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}.
\end{align}
To compute $v(x)$ and $v'(x)$, the Barycentric quadrature rule in
equation~\eqref{eqn:vvpQuadrature} is used. If $x \in \Omega^c$, the
identity
\begin{align}
\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{(y-a)^{-1}}{y-x} dy, 
\end{align}
is used, and the resulting Barycentric quadrature formula is
\begin{align}
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}}
    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Efficiently Applying Quadrature}
\label{s:fmm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Barycentric quadrature rule achieves acceptable accuracy for
computing the velocity, shear stress, and vorticity.  However, applied
directly, it requires $\mathcal{O}(N^2)$ operations.  Since the shear
stress must only be computed once per time step, and the vorticity is
only used as a post-processing step, we accept the $\mathcal{O}(N^2)$
algorithm.  However, the velocity must be computed at every GMRES
iteration, which would make the overall method impractical without a
fast algorithm.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Streamlines and Tortuosity}
\label{s:streamlines}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Having developed numerically accurate methods to compute the velocity
$\uu$ at points close to the bodies, we are able to compute the
trajectories of particles passing through an eroded body.  To find the
trajectory governed by equation~\eqref{eqn:trajectories}, we use the
fourth-order explicit Runge-Kutta method with a fixed time step size.
Since our method is both high-order in time and space, we are able to
simulate dynamics very close to the eroding bodies.  Resolving the flow
in these small velocity regions is essential to accurately describe
anomalous diffusion and mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.

{\color{red}
To calculate tortuosity $T$ numerically, we use the simple quaduature
rule
$$T=\frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N} u_x(y_i) \lambda(y_i) \Delta y_i}{\displaystyle\sum_{i=1}^{N} u_x(y_i) \Delta y_i},$$ 
where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section, we present the numerical simulations of dense packings
of eroding bodies.  The computational domain $\Omega$ is a rectangle
$[-3,3] \times [-1,1]$ with rounded off corners and we place bodies only
in $[-1,1] \times [-1,1]$.  For all simulations, we discretize $\Gamma =
\bd \Omega$ with $N_\out=1024$ points.  The Dirichlet boundary condition
on $\Gamma$ is a hagen-poiseuille flow.  As the bodies erode, the flow
rate is adjusted to maintain the physical constant pressure drop
boundary condition.  To maintain this pressure drop, we compute the
pressure at near the inlet and outlet at each time step as described in
our previous work~\cite{qua-moo2018}.

>>>>

\begin{itemize}
\item \cite{dar-mcc1998} show that if there is a region with high
porosity, this greatly affects the relationships between the porosity
and permeability.  Uses a Lattice-Boltzmann method.

\item Continuous Time Random Walks

\item Rothman in 1988 did CA for flow in 2D porous media

\item ``Canductivity and permeability af rocks" 1984

\item ``An Analytical Study on Natural Convection in Isotropic and .
Anisotropic Porous Channels" shows how anisotropy affects heat transfer
in porous media.

\item "The Effect of Anisotropic Permeability on Free Convective
Boundary Layer Flow in Porous Media" is the same as last bullet

\item Near-singular integration such as regularization, QBX, Lagrange
interpolation, panel-based quadrature, etc.

\end{itemize}

@@

Equation~\eqref{eqn:laplaceComplex} can be converted to a Cauchy
integral by first finding boundary data of $v$ which satisfies the
Sokhotski-Plemelj jump relation
\begin{align}
  \label{eqn:SPrelation}
  v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
\todo[inline]{Need to be careful about interior and exterior limits}
Once the boundary data of $v$ is formed, we have
\begin{align}
  \label{eqn:cauchy}
  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \quad
  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \quad
  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy.
\end{align}
for $x \in \Omega$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tortuosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The tortuosity of a geometry quantifies the average amount of turning
made by a streamline.  Mathematically, it is defined as
\begin{align}
  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_x(y)\lambda(y)\,dy}
  {\displaystyle\int_{S}u_x(y)\,dy},
  \label{eqn:tortuosity1}
\end{align}
where $S$ is an cross-section perpendicular to the $x$ axis with length
$d$, $\lambda(y)$ is the length of the streamline that is initialized
at the $y$-coordinate along $S$, and $u_x(y)$ is the $x$ component of
the velocity at the $y$-coordinate along $S$.  Following~\cite{}, the
trajectories are formed until they cross a second cross-section.  In our
work, we always initialize the trajectories at $x=-1$ and stop them when
they reach $x=1$.

Under the assumptions that the flow is incompressible and not reentrant,
the tortuosity can be equivalently measured as~\cite{dud-koz-mat2011}
\begin{align}
  T = \frac{\displaystyle\int_\Omega \|\uu(\yy)\|\, d\yy}
           {\displaystyle\int_\Omega u_x(\yy)\, d\yy}.
  \label{eqn:tortuosity2}
\end{align}
The flow is reentrant if all streamlines connect the inlet to the
outlet.  Recirculation zones are possible in viscous fluids, but they
only constitute a small fraction of the total porous media.  Therefore,
the tortuosity defined in equation~\eqref{eqn:tortuosity2} is an upper
bound for the definition in equation~\eqref{eqn:tortuosity1}.  We have
used formulas for a particular geometry, and the difference is
negligible.  Since equation~\eqref{eqn:tortuosity2} does not require the
additional work of computing particle trajectories, we use this
definition for the tortuosity.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pore Throat Size}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \item Pore throat sizes affect many things such as first passage time,
  mixing, chemical reactions, heat conduction, biological activities
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{s:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We have shown that the velocity, shear stress, and vorticity of the
double-layer potential can all be written in terms of Cauchy integrals
and its first two derivatives.  Therefore, we require quadrature methods
to evaluate the expressions in equation~\eqref{eqn:cauchy}.  Since the
integrands are all smooth and periodic, the trapezoid rule has spectral
accuracy.  However, the integrand becomes nearly singular as $x$
approaches $\bd\Omega$, and the quadrature error is arbitrarily large at
a fixed resolution.  There have been a variety of near-singular
integration schemes developed.   We opt to use a method first outlined
by Barnett et al.~\cite{bar-wu-vee2015} which we call the {\em
Barycentric quadrature rule}.  Quadrature rules for only the Cauchy
integral and its first derivative are presented, and we extend this
result to include the second derivative.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial Discretization}
\label{s:spatialDiscretization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
By using an integral equation formulation, we only have to discretize
the one-dimensional boundary of the domain.  Therefore, we easily
resolve complex geometries, and differentiation can be performed with
spectral accuracy in Fourier space.  We discretize each eroding body
$\gamma_k$ with $N_\iin$ points and discretize the outer wall $\Gamma$
with $N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ is
denoted by $\yy_j^0$, and the $j^{th}$ discretization point on
$\gamma_k$ is denoted by $\yy^k_j$.  The discretization points are
initially distributed evenly in arclength, and this equispacing is
maintained for the entire simulation by using a {\thL}
formulation~\cite{hou-low-she1994}.  In addition, we apply mild
smoothing strategies~\cite{qua-moo2018} to avoid the corners that
erosion inevitably develop.

Given these discretization points, the velocity at $\xx$ can be
approximated with the quadrature formula
\begin{align}
  \label{eqn:trap}
  \uu(\xx) \approx \sum_{j=1}^{N_\out} w^0_j D(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j,
\end{align}
$w^k_j$ are quadrature weights (which depend on $N_\iin$, $N_\out$, and
the lengths of $\gamma^k$), and $D$ is the kernel of the Stokes
double-layer potential defined in Equation~\eqref{eqn:stokesDLP}.
Matching the limiting behavior of the velocity with the boundary
condition, the density function at the quadrature point solves
\begin{align}
  \UU_\ell &= \sum_{j=1}^{N_\out} 
    w^0_j D(\yy^0_\ell,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin}
    w^k_j D(\yy^0_\ell,\yy^k_j) \eeta^k_j, 
    \quad \ell = 1,\ldots,N_\out \\
  0 &= \sum_{j=1}^{N_\out} 
    w^0_j D(\yy^m_\ell,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin} 
    w^k_j D(\yy^m_\ell,\yy^k_j) \eeta^k_j, 
    \quad \ell = 1,\ldots,N_\iin, \: m=1,\ldots,M. 
\end{align}

Once the density function is found at the quadrature points, the shear
stress and vorticity can be approximated.  In particular,
the deformation tensor is
\begin{align}
  \ssigma(\xx) = \frac{1}{2}(\nabla \uu + \nabla \uu^T) = 
\end{align}
and the vorticity is
\begin{align}
  w(\xx) = 
\end{align}

The choice of the quadrature rule determines the overall accuracy of the
method.  To simulate dense suspensions of eroding bodies, it is
imperative that the error of the chosen quadrature rule is bounded for
independent of the configuration of the bodies.  To achieve this goal,
we apply a Barycentric quadrature rule

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Barycentric quadrature rule developed by Barnett et
al.~\cite{bar-wu-vee2015} approximates the double-layer potential for
the velocity~\eqref{eqn:stokesDLP} with bounded error.  However, to
compute the shear stress and vorticity, the method must be extended.  We
first briefly describe the original Barycentric quadrature method, and
then derive a necessary extension to simulate erosion.  We present the
quadrature for a simply-connected domain $\Omega$, and the method
naturally extends to the eroding geometry by applying the quadrature to
each of its connected component.  The method starts with an underlying
quadrature rule, and we use the trapezoid rule because of its superior
accuracy for smooth periodic functions~\cite{tre-wei2014}.  Since the
quadrature points are uniformly distributed, the quadrature weights are
$w_j = L/N$, $j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.

We next identify all the discretization points, the normal vector, and
the density function with their complex-value counterparts.  Then, all
the layer potentials are a combination of a Cauchy integral and its
first two derivatives.  Given a density function $\tau(y)$, the boundary
data is solved using the Sokhotski-Plemelj jump
relation~\eqref{eqn:SPrelation}.  If $x \in \Omega$ is too close to
$\bd\Omega$ and the trapezoid rule is applied to the identity
\begin{align}
  v(x) = \int_{\bd\Omega} \frac{v^{-}(y)}{y-x} \, dy, 
  \quad x \in \Omega,
\end{align}
the quadrature error is large since the integrand has a large
derivative.  However, if the trapezoid rule is applied to
\begin{align}
  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0,
\end{align}
the quadrature error is bounded since the integrand and all its
derivatives are bounded with respect to $x$. That is,
\begin{align}
  \sum_{j=1}^{N} \frac{v^{-}(y_j) - v(x)}{y_j - x} w_j \approx 0.
\end{align}
Rearranging for $v(x)$, we have
\begin{align}
  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v^{-}(y_j)}{y_j - x} w_j}
  {\sum\limits_{j=1}^N \frac{1}{y_j - x} w_j}.
  \label{eqn:Baryv}
\end{align}
\todo[inline]{Need to cite work that Barnett et al. reference} 
To approximate $v'(x)$, the trapezoid rule is applied to the two
integrals in the identity
\begin{align}
  v'(x) = \frac{\int\limits_{\bd\Omega} 
    \frac{v^{-}(y) - v(x)}{(y-x)^2}\, dy}
  {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy},
\end{align}
resulting in the quadrature rule
\begin{align}
  v'(x) \approx \frac{\sum\limits_{j=1}^{N}
    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j}
  {\sum\limits_{j=1}^{N} \frac{1}{y_j-x} w_j}.
  \label{eqn:Baryvprime}
\end{align}

To compute the shear stress and vorticity, we require a Barycentric
quadrature rule for $v''(x)$.  Mimicking the construction of the
quadrature rule for $v(x)$ and $v'(x)$, we start with the second
derivative of the Cauchy integral theorem
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x).
\end{align}
Using the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
  \left\{
    \begin{array}{ll}
      1, & n = 1, \\
      0, & n > 1, \\
    \end{array}
  \right.
\end{align}
where $x \in \Omega$ and $n \in \mathbb{N}$, we have
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
      {(y-x)^3}\, dy.
\end{align}
This integrand is constructed so that it is bounded for all $x \in
\Omega$, and applying the trapezoid rule, we have
\begin{align}
  0 \approx  \sum_{j=1}^{N} 
      \frac{2v^{-}(y_j) - v''(x)(y_j-x)^2 - 2v(x) - 2(y_j-x)v'(x)}
      {(y_j-x)^3} w_j,
\end{align}
where the accuracy is independent of the proximity of $x$ to
$\bd\Omega$. Solving for $v''(x)$, the Barycentric quadrature rule for
the second derivative is
\begin{align}
  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}.
\end{align}
This formula requires accurate approximations of $v(x)$ and $v'(x)$, but
these are available in equations~\eqref{eqn:Baryv}
and~\eqref{eqn:Baryvprime}.

To apply the quadrature to multiply-connected domains, we must all
consider exterior points $x \in \Omega^c$.  Mimicking the construction
in~\cite{bar-wu-vee2015}, we use the quadrature rule
\begin{align}
\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{(y-a)^{-1}}{y-x} dy, 
\end{align}
is used, and the resulting Barycentric quadrature formula is
\begin{align}
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}}
    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}.
\end{align}
Again, values of $v(x)$ and $v'(x)$ are required, and these are
available in~\cite{bar-wu-vee2015}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Efficiently Applying the Quadrature}
\label{s:fmm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Barycentric quadrature rule achieves acceptable accuracy for
computing the velocity, shear stress, and vorticity.  However, applied
directly, it requires $\mathcal{O}(N^2)$ operations.  Since the shear
stress must only be computed once per time step, and the vorticity is
only used as a post-processing step, we accept the $\mathcal{O}(N^2)$
algorithm.  However, the velocity must be computed at every GMRES
iteration, which would make the overall method impractical without a
fast algorithm.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Streamlines and Tortuosity}
\label{s:streamlines}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Having developed numerically accurate methods to compute the velocity
$\uu$ at points close to the bodies, we are able to compute the
trajectories of particles passing through an eroded body.  To find the
trajectory governed by equation~\eqref{eqn:trajectories}, we use the
fourth-order explicit Runge-Kutta method with a fixed time step size.
Since our method is both high-order in time and space, we are able to
simulate dynamics very close to the eroding bodies (Figure~\ref{fig:}
\todo[inline]{reference a figure or two from the results section)}.
Resolving the flow in these small velocity regions is essential to
accurately describe anomalous diffusion and
mixing~\cite{leb-den-dav-bol-car-dec-bou2011}.

To calculate tortuosity $T$, we use the simple quadrature rule
\begin{align}
  T = \frac{1}{d}\frac{\displaystyle\sum_{i=1}^{N} 
    u_x(y_i) \lambda(y_i) \Delta y_i}
  {\displaystyle\sum_{i=1}^{N} u_x(y_i) \Delta y_i}, 
\end{align}
where $y_i$ is the point on $S$ and $\Delta y_i = y_{i+1}-y_{i}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Integration}
\label{s:time}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We reuse the time stepping method outlined in our previous
work~\cite{qua-moo2018}.  Rather than tracking the $(x,y)$
coordinates, the {\thL} variables are tracked. A second-order
Implicit-Explicit method is used. In particular, the diffusive term
corresponding to the curvature penalization term is discretized
implicitly, and all other terms, which are non-stiff, are treated
explicitly.

\todo[inline]{Talk about time integration for erosion and for tracers}
